New

### 2022-02-01 Writing/manuscript.rmd
modify

---
title: "New"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
abstract: ""
---

@@

```{r include = FALSE}
# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================
#* source all the functions in the Functions folder
fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
  lapply(., function(x) source(x))

#* read the results rds file
results <-
  here("Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff]

pi_dif_gwr <-
  results[, .(pi_dif = mean(pi_diff)), by = type] %>%
  .[, diff(pi_dif)]

#* create figures
source(here("Codes", "3_make_figures_publication.R"))
```

@@

<br />

<div id="refs"></div>

>>>>

---
title: "New"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: american-journal-of-agricultural-economics.csl
abstract: ""
---

@@

```{r include = FALSE}
# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================
#* source all the functions in the Functions folder
# fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
#   lapply(., function(x) source(x))
# 
# #* read the results rds file
# results <-
#   here("Results", "pi_data.rds") %>%
#   readRDS() %>%
#   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
#   .[, bias := pi_diff_est - pi_diff]
# 
# pi_dif_gwr <-
#   results[, .(pi_dif = mean(pi_diff)), by = type] %>%
#   .[, diff(pi_dif)]
# 
# #* create figures
# source(here("Codes", "3_make_figures_publication.R"))
```

@@
